---
title: "Palmer Penguins"
author: "James Jeberson"
date: "2024-03-23"
output: html_document
---

## Setting up my environment
Notes: Setting up my environment by loading the 'tidyverse' and 'palmerpenguins' packages

```{r loading packages, message=FALSE}
library(tidyverse)
library(palmerpenguins)
```

#Visualizations
Here we will go through a series of visualizations

## Flipper Length vs Body Mass by Species
Here we plot flipper length against body mass and look at the breakdown by species

```{r warning=FALSE}
ggplot(penguins) +
  geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g, color = species, shape = species)) +
  labs("text", x = "Flipper Length in mm", y = "Body Mass in g")
```

## Flipper Length vs Body Mass by Species
Here we plot flipper length against body mass and look at the breakdown in sex for each species

### Adelie Species
Here we plot flipper length against body mass and look at the breakdown in sex for **Adelie** species

```{r warning=FALSE}
penguins %>% 
  filter(species == "Adelie") %>% 
  ggplot() + 
  geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g, color = sex, shape = sex)) +
  labs("text", x = "Flipper Length in mm", y = "Body Mass in g")
```

### Chinstrap Species
Here we plot flipper length against body mass and look at the breakdown in sex for **Chinstrap** species

```{r warning=FALSE}
penguins %>% 
  filter(species == "Chinstrap") %>% 
  ggplot() + 
  geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g, color = sex, shape = sex)) +
  labs("text", x = "Flipper Length in mm", y = "Body Mass in g")
```

### Gentoo Species
Here we plot flipper length against body mass and look at the breakdown in sex for **Gentoo** species

```{r warning=FALSE}
penguins %>% 
  filter(species == "Gentoo") %>% 
  ggplot() + 
  geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g, color = sex, shape = sex)) +
  labs("text", x = "Flipper Length in mm", y = "Body Mass in g")
```

## Flipper Length vs Body Mass by Species & Island
Here we plot flipper length against body mass and look at the breakdown in species & island

```{r warning=FALSE}
ggplot(penguins) +
  geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g, color = species, shape = species)) +
  labs("text", x = "Flipper Length in mm", y = "Body Mass in g") +
  facet_wrap(~island)
```
